\documentclass[DM,authoryear,toc]{lsstdoc}
% lsstdoc documentation: https://lsst-texmf.lsst.io/lsstdoc.html
\input{meta}

%If you want glossaries
\input{aglossary.tex}
\makeglossaries

\title{Rubin Observatory Data Security Standards Implementation}

% Optional subtitle
% \setDocSubtitle{A subtitle}

\author{%
William O'Mullane,
Russ Allbery,
Yusra AlSayyad,
Eric Bellm,
Andy Clements,
Richard Dubois,
Joshua Hoblitt,
Cristi\'{a}n Silva,
Ian Sullivan,
Kian-Tat Lim,
Phil Marshall\\
Agency oversight: Ashley Zauderer-Vanderley (NSF), Helmut Marsiske (DOE)
}

\setDocRef{DMTN-199}
\setDocUpstreamLocation{\url{https://github.com/lsst-dm/dmtn-199}}

\date{2025-05-14}
%\date{\vcsDate}

% Optional: name of the document's curator
% \setDocCurator{The Curator of this Document}

\setDocAbstract{%
In this document we describe a set of measures that we plan to take, in order to secure the data taken at Rubin Observatory to the standards set by the US funding agencies.
}

% Change history defined here.
% Order: oldest first.
% Fields: VERSION, DATE, DESCRIPTION, OWNER NAME.
% See LPM-51 for version number policy.
\setDocChangeRecord{%
  \addtohist{0.1}{2021-07-19}{Unreleased. Set up structure}{William O'Mullane}
  \addtohist{0.2}{2021-09-28}{Unreleased. First draft for JSR 2021}{William O'Mullane}
  \addtohist{0.3}{2021-10-04}{Unreleased. Second draft for JSR 2021}{William O'Mullane}
  \addtohist{0.4}{2021-10-05}{Unreleased. Tidy for JSR 2021}{William O'Mullane}
  \addtohist{0.5}{2021-11-23}{Unreleased. Fix router price, include Huawei Avoid}{William O'Mullane}
  \addtohist{1.0}{2022-02-02}{Removed Huawei from this plan and added descriptions}{Victor Krabbendam}
  \addtohist{1.1}{2022-08-02}{Simplify summary in intro }{William O'Mullane}
  \addtohist{1.2}{2022-10-04}{Include notes on working with commissioning data}{Phil Marshall}
  \addtohist{1.3}{2022-10-26}{Embargo clarification}{William O'Mullane}
  \addtohist{2.0}{2023-06-08}{Updated Requirements from NSF and DOE. Include agency oversight.}{William O'Mullane, Bob Blum, Phil Marshall}
  \addtohist{2.1}{2024-07-12}{Removed mention of derivative catalogs}{Phil Marshall}
  \addtohist{2.2}{2024-08-02}{Remove compliance appendix - point to RTN-082}{William O'Mullane}
  \addtohist{2.3}{2024-09-16}{Make ComCam exemption explicit - tidy some embargo wording}{William O'Mullane, Phil Marshall}
  \addtohist{2.4}{2025-01-13}{80-hour embargo period in survey-mode LSSTCam commissioning.}{Phil Marshall}
}


\begin{document}

% Create the title page.
\maketitle
% Frequently for a technote we do not want a title page  uncomment this to remove the title page and changelog.
% use \mkshorttitle to remove the extra pages

% ADD CONTENT HERE
\input{body}
\newpage
\appendix


\newpage
% Include all the relevant bib files.
% https://lsst-texmf.lsst.io/lsstdoc.html#bibliographies
\section{References} \label{sec:bib}
\renewcommand{\refname}{} % Suppress default Bibliography section
\bibliography{local,lsst,lsst-dm,refs_ads,refs,books}

% Make sure lsst-texmf/bin/generateAcronyms.py is in your path
\section{Acronyms and Glossary} \label{sec:acronyms}
%\input{acronyms.tex}
% If you want glossary uncomment below -- comment out the two lines above
\printglossaries





\end{document}
